\thispagestyle{plain}
\section{Introduction}

In systems biology, biological systems are modelled mathematically in order to predict the behaviour of the system \cite{intro_computational_systems_biology}. An important and fundamental system is the cell and its metabolism.
Due to advances in technology, detailed information about different cells and organisms is available. Based on this data, genome-scale models can be constructed. Metabolic networks are genome-scale models which capture the interactions between entities in the cell such as small molecules (metabolites) and enzymes~\cite{intro_computational_systems_biology}. 
A commonly used approach to study metabolic networks are constraint-based methods, where we assume a steady-state of metabolites within the cell, which means that the production and consumption of each metabolite is balanced \cite{palsson_systems_biology}. The steady-state assumption, together with bounds on the flux through each reaction, defines a system of linear constraints. A solution corresponds to the flux distribution, which is the rate of each reaction, that satisfies the constraints \cite{intro_computational_systems_biology}. \\ %flow of metabolites through a metabolic network using mathematical optimization
A basic method to analyse the flux distribution in a metabolic network is flux balance analysis (FBA) \cite{FBA}. In FBA, a linear program is solved where we optimise a biological objective function, such as maximising growth. As cells evolve under selection pressure, it is plausible that the behaviour is in line with a biological objective and using mathematical optimization to study the flow of metabolites through a metabolic network is reasonable \cite{palsson_systems_biology}. With FBA it is possible to predict cellular behaviour in accordance with observations in experiments \cite{FBA}. \\
%% MOTIVATION AND CONTEXT 1-2 pages
%% get attention and introduce topic
%% background information
% \todo[inline]{question addressed system biology}
% System biologists model large biological systems with the help of mathematical approaches to predict the behaviour of the system \cite{intro_computational_systems_biology}. 
% \todo[inline]{goal of modelling}
% \todo[inline]{question addressed with studying metabolic models} 
% \todo[inline]{metabolic models}
% \todo[inline]{availability of GEMs}
% Due to advances in technology, 
% quantitative data on biological systems.... detailed information of the cell ...
% We have access to the composition of ... give rise to reconstructed biochemical reaction networks \cite{palsson_systems_biology}.
% \todo[inline]{metabolic network}
% \todo[inline]{FBA} 
% Flux balance analysis is an approach for analyzing the flow of metabolites through a metabolic network using mathematical optimization \cite{FBA}.
% \todo[inline]{success and use of FBA}
% \todo[inline]{problems with FBA}
However, solutions of FBA often violate the loop law, which means that the solution contains internal cycles which is biologically not plausible. Loopless FBA (ll-FBA) is an extension to FBA which includes thermodynamic information \cite{elimination_infeasible_loops}. A solution to ll-FBA does not contain internal cycles, but ll-FBA is computationally harder as we need to solve a disjunctive program, which is usually reformulated as a mixed-integer program (MIP). 
In this thesis, we look at different reformulations of ll-FBA and compare the performance of different MIP techniques. \todo[inline]{MIP technique correct for all/most approaches?}

%% thesis statement: topic, question being addressed, summarize resulst and significance
%% STRATEGY 1 page: what am I trying to do

%% OUTLINE 1/2 page
%% and outlines structure to come
% \todo[inline]{overview of thesis}

In \cref{section:optimization}, we will give a short introduction into mathematical optimization and present the aspects relevant for this thesis including the concept and solving strategies for linear programming, mixed-integer programming and disjunctive programming. In \cref{section:metabolic_networks}, we will motivate the biological context in more detail and present the relevant constrained-based methods in detail. 
The methods used are presented in \cref{section:methods} including a combinatorial Benders' approach and intersection cuts for ll-FBA. In \cref{section:results}, we present and discuss the computational results. 

\todo[inline]{FBA extensions}

\input{Chapters/notation}
